---
output:
  md_document:
    variant: markdown_github
---

# photomoe

A simple package for downloading and collaging photos from online sources.  `magick` does all the heavy lifting. You can download the development version from GitHub with:

```{r eval=FALSE}
devtools::install_github("jaytimm/photomoe")
```



## Download images

```{r include=FALSE}
library(tidyverse)
```


```{r message=FALSE, warning=FALSE}
tweet_pics <- rtweet::search_tweets("#standwithukraine", 
                                    n = 1000, 
                                    include_rts = F) %>%
  filter(!is.na(media_url)) 
```


```{r message=FALSE, warning=FALSE}
photomoe::img_download_images(link = unlist(tweet_pics$media_url)[1:49], 
                              dir = tempdir(), 
                              prefix = 'uk', 
                              scale_border = T)
```




## Build collage

The `img_build_collage` function builds a collage per a user specified directory of images -- based on the `magick` package and this [very nice post](https://masalmon.eu/2017/03/19/facesofr/).   

### #standwithukraine

```{r fig.height=6, message=FALSE, warning=FALSE}
photomoe::img_build_collage(dir = tempdir(), 
                            dimx = 7, 
                            dimy = 7, 
                            prefix = 'uk')
```




## Google image links

```{r fig.height=6, message=FALSE, warning=FALSE}
search1 <- 'pointing at rainbows'
search2 <- 'piano keys'
links <- lapply(list(search1, search2), 
                photomoe::img_get_gurls)

head(links[[1]])
```


### pointing at rainbows

```{r}
photomoe::img_download_images(link = links[[1]], 
                              dir = tempdir(), 
                              prefix = search1, 
                              scale_border = T)

photomoe::img_build_collage(dir = tempdir(), 
                            dimx = 5, 
                            dimy = 4, 
                            prefix = search1)
```


### piano keys

```{r echo=FALSE}
photomoe::img_download_images(link = links[[2]], 
                              dir = tempdir(), 
                              prefix = search2, 
                              scale_border = T)

photomoe::img_build_collage(dir = tempdir(), 
                            dimx = 5, 
                            dimy = 4, 
                            prefix = search2)
```
